---
title: "Beth's mixed results: isolated items and pairs"
output:
  word_document:
    reference_docx: template.docx
  pdf_document: default
---

Date: `r Sys.Date()`

<br>

<!-- loading packages, user-defined functions and datasets -->
```{r echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, include=FALSE}
libs <- c("magrittr", "tidyverse", "knitr",
          "lme4", "sjstats", "TMB")
lapply(libs, require, character.only = TRUE)
load(file="ws_09_10_18.RData")
```

<br>

<!-- set folder for graphs -->
```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
df_isolated %<>%
  filter(age_month <= 131)

df_isolated_item %<>%
  filter(age_month <= 131)

df_isolated_pair %<>%
  filter(age_month <= 131)

df_mixed_recalled %<>%
  filter(age_month <= 131)

#  fit models
mod_item1 <- glmer(recalled ~ stimulus_type + age_month + (1 | id),
             data = df_isolated_item, family = binomial)
mod_item2 <- glmer(recalled ~ stimulus_type * age_month + (1 | id),
                   data = df_isolated_item, family = binomial)

mod_pair1 <- glmer(recalled ~ stimulus_type + age_month + (1 | id),
                  data = df_isolated_pair, family = binomial)
mod_pair2 <- glmer(recalled ~ stimulus_type * age_month + (1 | id),
                  data = df_isolated_pair, family = binomial)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
#  functions for tables
p_value_table <- function(model, interaction = FALSE) {
  if (interaction == TRUE) {
    summary_model <- tibble(Coefficient = c("Intercept", "Stimulus Type", "Age" , "Stimulus Type * Age"), 
                            `Odds Ratios` = exp(fixef(model))) 
  } else {
    summary_model <- tibble(Coefficient = c("Intercept", "Stimulus Type", "Age"), 
                            `Odds Ratios` = exp(fixef(model))) 
  }
  
  summary_model %>%
    cbind(exp(confint(model)) %>% 
            as_tibble() %>% 
            slice(2:n()) %>%
            select_all(.funs = funs(paste0("CI ", .)))) %>%
    (function(x) {
      p_values = p_value(model, p.kr = TRUE)$p.value
      
      cbind(x, tibble(`p-value` = ifelse(p_values < 0.001, "<0.001", round(p_values, 3))))
    }) %>%
    rename(`Lower CI 95%` = `CI 2.5 %`, `Upper CI 95%` = `CI 97.5 %`) %>%
    round_df(3) %>%
    kable()
}

r2_table <- function(df, model) {
  tibble(Observations = df %>% nrow(),
         `Marginal R2` = r2(model)[[1]],
         `Conditional R2` = r2(model)[[2]]) %>%
    round_df(3) %>%
    kable()
}

random_effects_table <- function(model) {
  tibble(`Random effects` = c("σ2", "τ00 Child ID", "ICC Child ID"),
       Value = c(re_var(model), icc(model))) %>%
  round_df(3) %>%
  kable()
}

mod_comparison_table <- function(model1, model2) {
  comparison <- anova(model1, model2)
  comparison %>% as_tibble() %>% round_df(3) %>%
    kable()
}
```


#### Demographic info of the sample
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_isolated[!duplicated(df_isolated$id),] %>%
  (function(x) {
    tibble(Participants = nrow(x),
           `M age month` = mean(x$age_month),
           `Range age month` = paste(c(min(x$age_month), max(x$age_month)), collapse = ", "),
           Boys = nrow(filter(x, gender == "M")))
  }) %>%
  round_df(1) %>%
  kable()
```

<br>

#### model isolated item 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
p_value_table(mod_item1)
```

<br>

#### model isolated item 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
p_value_table(mod_item2, interaction = TRUE)
```

<br>

#### model isolated pair 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
p_value_table(mod_pair1)
```

<b>

#### model isolated pair 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
p_value_table(mod_pair2, interaction = TRUE)
```

<br>

#### r2 isolated item 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
r2_table(df_isolated_item, mod_item1)
```

<br>

#### r2 isolated item 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
r2_table(df_isolated_item, mod_item2)
```

<br>

#### r2 isolated pair 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
r2_table(df_isolated_pair, mod_pair1)
```

<br>

#### r2 isolated pair 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
r2_table(df_isolated_pair, mod_pair2)
```

<br>

#### random effects isolated item 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
random_effects_table(mod_item1)
```

<br>

#### random effects isolated item 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
random_effects_table(mod_item2)
```

<br>

#### random effects isolated pair 1
```{r echo=FALSE, warning=FALSE, message=FALSE}
random_effects_table(mod_pair1)
```

<br>

#### random effects isolated pair 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
random_effects_table(mod_pair2)
```

<br>

#### model comparison isolated item
```{r echo=FALSE, warning=FALSE, message=FALSE}
mod_comparison_table(mod_item1, mod_item2)
```

<br>

#### model comparison isolated pair
```{r echo=FALSE, warning=FALSE, message=FALSE}
mod_comparison_table(mod_pair1, mod_pair2)
```

<br>

#### isolated items plot
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5}
isolated_plot <- function(df, title, stimulus_type_label) {
  df %>%
    group_by(id, age_month, stimulus_type) %>%
    mutate(recalled = recalled %>% as.character() %>% as.integer()) %>%
    summarize(recalled_total = sum(recalled)) %>%
    ggplot(aes(x = age_month, y = recalled_total, shape = stimulus_type, linetype = stimulus_type)) +
    geom_jitter(height = 0.25, width = 0.25) +
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Age in months", y = paste("Number of ", stimulus_type_label, " accurately recalled", sep = "")) +
    geom_smooth(method='lm', colour = 'black', size = 0.3) +
    scale_shape_manual(name = "List", labels = c("Digits", "Words"), values = c(0, 3)) + 
    scale_linetype_manual(name = "List", labels = c("Digits", "Words"), values = c("solid", "dotted")) 
}

isolated_plot(df_isolated_item, "Isolated items", "items")
```

<br>

#### isolated pairs plot
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5}
isolated_plot(df_isolated_pair, "Isolated pairs", "pairs")
```

<br>

#### total of mixed lists recalled
```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=7, fig.height=5}
ggplot(df_mixed_recalled, aes(x=age_month, y=recalled_total)) +
  geom_jitter(height = 0.25, width = 0.25, size = 0.3) +
  geom_smooth(method='lm', colour = 'black', size = 0.3) +
  ggtitle("Mixed lists") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Age in months", y = paste("Number of mixed lists recalled", sep = "")) +
  scale_y_continuous(limits=c(-0.3,8))
```
